\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-11-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
edit the z position of the target

We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
starting from the beam line towards larger radius:\\
\begin{itemize}
  \item The 6~atm $^4$He target forms the detector central z-axis which is 
     along the beamline ; it is a 284~mm long, 6~mm diameter Kapton straw with 
     a 27~$\mu$m wall.
   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o{}ller electrons scattered by the beam. This region is surrounded by 
      a 4 $\mu$m thick window made of grounded aluminized Mylar.
   \item The second gas gap region extends between 20~mm and 30~mm and is 
      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
      (DME).  This region is surrounded by a 4~$\mu$m thick window made of 
      aluminized Mylar set at $-4260$~V to serve as the cathode.
   \item The drift region is filled with the same Ne-DME gas mixture and 
      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
      The average electric field in this region is perpendicular to the beam 
      and about 550~V/cm.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
      275~V bias is applied across each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charges 
      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
      directly on its outer side and transmit the signal to the data 
      acquisition electronics.
\end{itemize}

>>>>

We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
starting from the beam line towards larger radius:\\
\begin{itemize}
  \item The 6~atm $^4$He target extends along the beamline forming the detector 
     central axis; it is a 292~mm~long, 6~mm diameter Kapton straw with a 
     27~$\mu$m wall. The detector and the target are centered at 64~cm to the 
     left of CLAS's center.
   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o{}ller electrons scattered by the beam. This region is surrounded by 
      a 4 $\mu$m thick window made of grounded aluminized Mylar.
   \item The second gas gap region extends between 20~mm and 30~mm and is 
      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
      (DME).  This region is surrounded by a 4~$\mu$m thick window made of 
      aluminized Mylar set at $-4260$~V to serve as the cathode.
   \item The drift region is filled with the same Ne-DME gas mixture and 
      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
      The average electric field in this region is perpendicular to the beam 
      and about 550~V/cm.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
      275~V bias is applied across each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charges 
      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
      directly on its outer side and transmit the signal to the data 
      acquisition electronics.
\end{itemize}
